---
title: "FARS Vignette"
author: "Luc Langevin"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{FARS Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The FARS package allows the analysis of data from the US National Highway Traffic Safety Administration's (Fatality Analysis Reporting System).  

This R package is available on Github and can be installed and used by typing those commands:  
```{r eval = FALSE}
devtools::install_github("https://github.com/llangevin/FARS")
library(countytimezones)
```

There are 3 functions that can be utilized for the analysis:  
- fars_read()  
- summarize_years()  
- fars_map_state()  

The function "fars_read()" reads a csv file of the accidents and generate a tibble file than can be used to analyse the data with R functions.  
```{r eval = FALSE}
data <- fars_read(filename = "./accident_2013.csv.bz2")
```

The function "summarize_years()" produce a summary of the accidents per year(s) for each month.
```{r eval = FALSE}
summarize_years<-fars_summarize_years(years=2013:2015)
```

The function "fars_map_state()" allows to see the accidents location on a map of the choosen state and year.

```{r eval = FALSE}
fars_map_state(40, 2014)
```

The accidents data for years 2013 to 2015 are available in the package "inst/extdata".
